---
title: "eda"
author: "Chris Peralta"
date: "January 31, 2019"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytext)
source("R/import_books.R")
source("R/import_characters.R")
source("R/import_alias.R")
source("R/standardize_names.R")
english_words <- read_csv("data/words_alpha.txt")
places <- read_csv("data/places.txt")
```

Find more names:
Getting variations of names and combining lists. 
```{r}
names_and_aliases <- characters %>% 
  select(name) %>% 
  bind_rows(rename(select(alias, aliases), name = aliases)) %>% 
  distinct()

#The removed code below is unnecessary and wastes time
get_name_variations <- function(name_data){
  name_data <- name_data %>% 
    mutate(name = str_trim(name), 
           name = str_squish(name))
  
  # plural <- name_data %>% 
  #   mutate(name = paste0(name, "s"))
  # 
  # possessive <- name_data %>% 
  #   mutate(name = paste0(name, "'s"))
  # 
  # possessive_s <- name_data %>% 
  #   mutate(name = paste0(name, "'"))
   
  short_name <- name_data %>% 
    mutate(name = str_split(name, " ")) %>% 
    unnest() %>% 
    anti_join(stop_words, by = c("name" = "word")) %>% 
    anti_join(mutate(stop_words, word = str_to_title(word)), by = c("name" = "word"))
  
  # short_name_plural <- short_name %>% 
  #   mutate(name = paste0(name, "s"))
  # 
  # short_name_possessive <- short_name %>% 
  #   mutate(name = paste0(name, "'s"))
  # 
  # short_name_possessive_s <- short_name %>% 
  #   mutate(name = paste0(name, "'"))
    
  bind_rows(name_data, short_name) %>% 
            #plural, possessive, possessive_s, short_name_plural,
            #short_name_possessive, short_name_possessive_s) %>% 
    distinct()
}
```

Co-occurences: 
Use ngrams
Compare all of them against name variations
Remove all rows without names
Shrink everything horizontally
(at this point there is a dataframe of names)
Can make a network graph at this point
Remove duplicate names within each rows and names that match themselves

Co-occurences through ngrams with / without dialogue 
This is a minimal working example
```{r}
all_names <- get_name_variations(names_and_aliases) %>% 
  mutate(name = str_remove(name, "^The ")) %>% 
  filter(!str_detect(name, "^.{1,3}$")) %>%
  filter(name != "", name != "Doubt", name != "Imperial", name != "House", 
         name != "Wait", name != "Lying", name != "Felis", name != "Seventh", 
         name != "Twelfth", name != "Dead", name != "Jaghut", name != "Darkness",
         name != "Ghost", name != "Mortal", name != "Sword", name != "Shield", 
         name != "Anvil", name != "Master", name != "Deck", name != "Cold", 
         name != "Moon", name != "Mage", name != "Iron", name != "Soon", 
         name != "Throw", name != "Fire", name != "Lady", name != "Mage", 
         name != "Seer", name != "Lieutenant", name != "Breath", name != "Sort",
         name != "Pale", name != "Councilman", name != "Sergeant", name != "High Fist",
         name != "Elder", name != "Green", name != "Pig", name != "Hound", 
         name != "Shadow", name != "Queen", name != "Dark", name != "Whirlwind", 
         name != "Dryjhna", name != "Black", name != "Captain", name != "High", 
         name != "Fist", name != "Assassin", name != "Last", name != "Bear", 
         name != "One", name != "King", name != "Silent", name != "Esta", 
         name != "Lord", name != "D'Arle", name != "Life", name != "Will", 
         name != "White", name != "Artist", name != "Treat", name != "Cook", 
         name != "Fish", name != "Setral", name != "Crippled", 
         !str_detect(name, "^[a-z]")) %>% 
  arrange(desc(nchar(name))) %>% 
  pull(name)

tictoc::tic()
temp <- books %>% 
  mutate(line = str_replace_all(line, 
                                fixed("Hood’s breath", ignore_case = TRUE), 
                                "Replacement")) %>% 
  standardize_names() %>% 
  unnest_tokens(ngram, line, token = "ngrams", n = 30, to_lower = FALSE) %>%
  filter(str_detect(ngram, pattern = fixed(all_names))) %>% 
  select(ngram) %>% 
  #apply(1, function(x) str_extract(x, pattern = fixed(all_names$name))
  apply(1, function(x){
              map_chr(all_names,
                  function(pat){
                    name <- str_extract(x, pattern = fixed(pat))
                    x <<- str_remove(x, pattern = fixed(pat))
                    name
                  })
                 })
  #rowwise() %>% 
  #do(chars = str_extract(.$ngram, pattern = fixed(all_names$name)))
  #mutate(chars = str_extract(ngram, pattern = fixed(all_names$name)))
tictoc::toc()


temp1 <- temp %>% 
  t() %>% 
  as.tibble() %>% 
  unite("names", V1:V3106, sep = ",")

temp2 <- temp1 %>% 
  mutate(names = str_replace_all(names, "NA", ","), 
         names = str_replace_all(names, ",+", ","), 
         names = str_remove_all(names, "^,|,$"), 
         names = str_replace_all(names, "Empress", "Laseen"), 
         names = str_replace_all(names, "Imperial Historian Duiker|Imperial Historian|Historian|Duiker", "Duiker"),
         names = str_replace_all(names, "Laseen Laseen", "Laseen"),
         names = str_replace_all(names, "Emperor Kellanved|Kellanved|Shadowthrone", 
                                 "Ammanas"), 
         names = str_replace_all(names, "Surly", "Laseen"),
         names = str_replace_all(names, "Paran|Ganoes Paran", "Ganoes Stabro Paran"), 
         names = str_replace_all(names, "Korbolo", "Korbolo Dom"),
         names = str_replace_all(names, "Rake", "Anomander Rake"), 
         names = str_replace_all(names, "Anomander Anomander", "Anomander"),
         names = str_replace_all(names, "Dujek", "Dujek Onearm"), 
         names = str_replace_all(names, "Onearm Onearm", "Onearm"), 
         names = str_replace_all(names, "Quick Ben|Quick", "Ben Adaephon Delat"),
         names = str_replace_all(names, "Crokus Younghand|Crokus|Cutter", 
                                 "Crokus Younghand"),
         names = str_replace_all(names, "Iskaral", "Iskaral Pust"), 
         names = str_replace_all(names, "Pust Pust", "Pust"), 
         names = str_replace_all(names, "Pust", "Iskaral Pust"), 
         names = str_replace_all(names, "Iskaral Iskaral", "Iskaral"),
         names = str_replace_all(names, "Caladan|Brood|Warlord", "Caladan Brood"), 
         names = str_replace_all(names, "Caladan Brood Caladan Brood", 
                                 "Caladan Brood"),
         names = str_replace_all(names, "Sergeant ", ""), 
         names = str_replace_all(names, "Talo Krafar|Talo", "Talo Krafar"),
         names = str_replace_all(names, "Osserc", "Osseric"), 
         names = str_replace_all(names, "Hound Gear", "Gear"), 
         names = str_replace_all(names, "Salk Elan", "Pearl"), 
         names = str_replace_all(names, "Heboric Light Touch|
                                 Heboric Ghost Hands|Heboric", 
                                 "Heboric Light Touch"), 
         names = str_replace_all(names, "Prazek Goul|Prazek", "Prazek Goul"), 
         names = str_replace_all(names, "Mesker Setral|Mesker", "Mesker Setral"),
         names = str_replace_all(names, "Kadagar Fant|Kadagar|Fant", "Kadagar Fant"),
         names = str_replace_all(names, "Silchas Ruin|Silchas", "Silchas Ruin"),
         connections = lengths(str_split(names, ","))) 
temp2 %>% mutate(names = str_split(names, ",")) %>% unnest() %>% distinct(names) %>% View

temp2 <- temp2 %>% 
  separate(names, into = paste0("name", 1:30), sep = ",")

library(ggraph)
library(igraph)

important_labels <- temp1 %>% 
  mutate(names = str_replace_all(names, "NA", "-"), 
         names = str_replace_all(names, "-+", ","), 
         names = str_remove_all(names, "^,|,$"),
         names = str_split(names, ","),
         connections = lengths(names)) %>% 
  filter(connections > 9) %>% 
  unnest() %>% 
  pull(names) %>% 
  unique()

tempgraph <- temp2 %>% 
  filter(connections > 1) %>% 
  graph_from_data_frame(directed = FALSE) %>% 
  ggraph() + 
  geom_edge_fan(spread = 5) + 
  geom_node_point() + 
  geom_node_text(aes(label = name, #alpha = (name %in% important_labels)), 
                 repel = TRUE, segment.size = 1, 
                 segment.color = "pink", color = "blue")) + 
  theme_void() + 
  theme(legend.position="none")
```



```{r eval=FALSE}
books %>% 
  unnest_tokens(ngram, line, token = "ngrams", n = 20, to_lower = FALSE) %>% 
  filter(str_detect(ngram, pattern = fixed(all_names$name))) %>% 
  separate(ngram, c(paste0("word", 1:20)), sep = " ") %>% 
  #filter(word1 %in% all_names$name) %>% 
  View()
#OR
#This approach seems better
books %>% 
  unnest_tokens(ngram, line, token = "ngrams", n = 10, to_lower = FALSE) %>% 
  separate(ngram, c(paste0("word", 1:10)), sep = " ") %>% 
  filter(word1 %in% all_names$name |
         word2 %in% all_names$name |
         word3 %in% all_names$name |
         word4 %in% all_names$name |
         word5 %in% all_names$name |
         word6 %in% all_names$name |
         word7 %in% all_names$name |
         word8 %in% all_names$name |
         word9 %in% all_names$name |
         word10 %in% all_names$name) %>% 
  View()
```
what happens when you put a vector as pattern in str_detect? 

Consider adding a column for which characters appear in which books, this will prevent characters such as the Assail, sorry, etc... being over represented. Get further toward the network graph before you worry about this. 

Some preprocessing:  (necessary?)
Remove titles from character names
Replace aliases with names
Remove dialogue
Replace pronouns with names??
Replace titles with names??



Code for dealing with lists when str_extract_all returns a lot of lists
```{r eval=FALSE}
temp1 <- compact(temp)
temp1 <- map(temp1, compact)
temp1 <- map(temp1, as.character)

temp1 <- temp %>% 
  compact() %>% 
  map(compact) %>% 
  map(as.character)

bind_rows(lapply(vectorList, as.data.frame.list)) %>% 
#as.data.frame(do.call(rbind, temp1)) %>% 
  as.tibble() %>% 
  View()

temp %>%   
  filter(!identical(chars, character(0))) %>% 
  View()

temp %>% 
  select(chars) %>% 
  mutate(chars2 = Filter(function(x) !identical(character(0),x), chars))

temp %>% 
  select(chars) %>% 
  mutate(chars = compact(chars)) %>% 
  View()

temp %>% 
  compact() %>% 
  View()

temp mutate(map str_extract() along character list on each line)
```
