---
title: "eda"
author: "Chris Peralta"
date: "January 31, 2019"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytext)
source("R/import_books.R")
source("R/import_characters.R")
source("R/import_alias.R")
source("R/standardize_names.R")
```

Find more names:
Getting variations of names and combining lists. 
```{r}
names_and_aliases <- characters %>% 
  select(name) %>% 
  bind_rows(rename(select(alias, aliases), name = aliases)) %>% 
  distinct()

get_name_variations <- function(name_data){
  name_data <- name_data %>% 
    mutate(name = str_trim(name), 
           name = str_squish(name))
   
  short_name <- name_data %>% 
    mutate(name = str_split(name, " ")) %>% 
    unnest() %>% 
    anti_join(stop_words, by = c("name" = "word")) %>% 
    anti_join(mutate(stop_words, word = str_to_title(word)), by = c("name" = "word"))

  bind_rows(name_data, short_name) %>% 
    distinct()
}
```

Co-occurences: 
Use ngrams
Compare all of them against name variations
Remove all rows without names
Shrink everything horizontally
(at this point there is a dataframe of names)
Can make a network graph at this point
Remove duplicate names within each rows and names that match themselves

Co-occurences through ngrams with / without dialogue 
This is a minimal working example
```{r}
all_names <- get_name_variations(names_and_aliases) %>% 
  mutate(name = str_remove(name, "^The ")) %>% 
  filter(!str_detect(name, "^.{1,3}$")) %>%
  filter(name != "", name != "Doubt", name != "Imperial", name != "House", 
         name != "Wait", name != "Lying", name != "Felis", name != "Seventh", 
         name != "Twelfth", name != "Dead", name != "Jaghut", name != "Darkness",
         name != "Ghost", name != "Mortal", name != "Sword", name != "Shield", 
         name != "Anvil", name != "Master", name != "Deck", name != "Cold", 
         name != "Moon", name != "Mage", name != "Iron", name != "Soon", 
         name != "Throw", name != "Fire", name != "Lady", name != "Mage", 
         name != "Seer", name != "Lieutenant", name != "Breath", name != "Sort",
         name != "Pale", name != "Councilman", name != "Sergeant", name != "High Fist",
         name != "Elder", name != "Green", name != "Pig", name != "Hound", 
         name != "Shadow", name != "Queen", name != "Dark", name != "Whirlwind", 
         name != "Dryjhna", name != "Black", name != "Captain", name != "High", 
         name != "Fist", name != "Assassin", name != "Last", name != "Bear", 
         name != "One", name != "King", name != "Silent", name != "Esta", 
         name != "Lord", name != "D'Arle", name != "Life", name != "Will", 
         name != "White", name != "Artist", name != "Treat", name != "Cook", 
         name != "Fish", name != "Setral", name != "Crippled", name != "Claw", 
         name != "Grin", name != "Witch", name != "Ceda", name != "Light", 
         name != "Warleader", name != "Warlock", name != "Bone", name != "Sengar", 
         name != "Grey", name != "Sister", name != "Corporal", name != "Dying", 
         name != "Commander",
         !str_detect(name, "^[a-z]")) %>% 
  arrange(desc(nchar(name))) %>% 
  pull(name)

temp0 <- books %>% 
  standardize_names_book() %>% 
  group_by(book, chapter) %>% 
  unnest_tokens(ngram, line, token = "ngrams", n = 20, to_lower = FALSE) %>%
  nest() %>% 
  ungroup() 

#source("extract-names.R") # Read below
```
At this point I had a lot of trouble writing code that could efficiently extract the co-occurence data from the books. In `extract-names.R` you'll see the code I used to extract the co-occurence data. The code is written quite poorly, because I wanted to keep the code simple for debugging purposes. It took me multiple attempts to extract all of the data and the final code took about 50 hours to run through all of the data and write all of the co-occurence data to .rds files. 

```{r}
pre_network_data <- list.files("data/network_data") %>% 
  map_df(~read_rds(paste0("data/network_data/", .))) %>% 
  remove_NAs() %>% 
  filter(names != "", 
         str_detect(names, ";")) %>%
  standardize_names_net() %>% 
  distinct(names, book, chapter) # Removes duplicate observations 
#Start at n=117 with Ibra Gholan

write_rds(pre_network_data, path = "data/pre_network_data.rds", compress = "none")
write_csv(pre_network_data, "data/pre_network_data.csv")

network_data <- pre_network_data %>% 
  separate(names, into = paste0("name", 1:21), sep = ";")

write_rds(network_data, "data/network_data.rds", compress = "none")
write_csv(network_data, "data/network_data.csv")
```


